---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# logdec - Verbosity using comments <a href="https://github.com/program--/logdec"><img src="man/figures/logo.svg" align="right" height="200"/></a>

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/logdec)](https://CRAN.R-project.org/package=logdec)
![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![MIT License](https://img.shields.io/badge/license-MIT-blue.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->



## Installation

You can install the development version from GitHub using `pak` or `remotes`:

``` r
# With `pak`
pak::pkg_install("program--/logdec")

# With `remotes`
remotes::install_github("program--/logdec")
```

## Usage

You can start using `logdec` quickly by adding `logdec::output()` to the top
of your `.R` file. Then, start adding comments using the `#>>` tag. Once your
logdec comments are in place, you can `source` the file as normal! Below is a clear
example of how logdec functions:

``` r
# example.R
options(logdec.engine = "cli")
logdec::output()

#>> Hello from {.pkg logdec}!
Sys.sleep(3)
#>> @info {.strong logdec} allows you to create output messages {cli::col_blue(\"directly\")} from comments!
Sys.sleep(3)
#>> @info All you need to do is install {.strong logdec}, then call {.fn logdec::output} at the top of your R file.
Sys.sleep(3)
#>> @info You can even use glue to pass variables to your comments! Here's some random value from {.fn rnorm}: {.val {rnorm(1)}}
Sys.sleep(3)
#>> @warning However, there are {cli::col_yellow(\"some limitations\")}, such as with console and package development use.
Sys.sleep(3)
#>> @success There are ways to work around this though, such as with the {.code %>>%} operator though!
Sys.sleep(3)
#>> Make your code output a bit easier to manage, with {.pkg logdec}! {cli::col_red(cli::symbol$heart)}
```

![](man/figures/example.svg)

If you notice, at the top of `example.R`, you can set the `logdec.engine` option
to one of the support engines. You can list all engines by calling:

```{r}
logdec::list_engines()
```

## Limitations
Since `logdec` attempts to read a file for specific comments, **console/interactive use is not available**.
However, to work around this issue, `logdec` includes an `extraction` operator (`%>>%`). This operator works
in either the conventional operator style, or in a functional style. See below for an example:

```r
options(logdec.engine = "cli")
library(logdec)

# Conventional Use:
# --------------------
"@info" %>>% "Output some form of informational message"
#> ℹ Output some form of informational message

"" %>>% "This will also work, but is a bit odd"
#> → This will also work, but is a bit odd

# Functional Use:
# --------------------
`%>>%`("@success Successfully outputted this!")
#> ✔ Successfully outputted this!

`%>>%`("@success", "Outputted again!")
#> ✔ Outputted again!
```
